---
title: "GJAM-test"
author: "Michelle DePrenger-Levin"
date: "May 4, 2017"
output: html_document
---

Generalized Joint Attribute Modeling

```{r setup, include=FALSE}
install.packages("gjam")
install.packages("neotoma")
```

Y matrix is the input
continuous abundance 
descrite abuncance, counts
relative counts...

```{r}
library(gjam)
library(neotoma)
library(ggplot2)
library(plyr)
```

# Gather data from Neotoma   
<http://www.openquaternary.com/articles/10.5334/oq.ab/> 
Pliocene to Holocene (and Anthropocene)      
Pollen databases- European and NA, and paleo data   
R packages:    
  - analogue  paleoecological data
  - rioja  paleoenviron     
  - Bchron radiocarbon dating   
  - paleofire  charcoal data   
  - neotoma  uses API to send data requests to Neotoma
```{r}
all.sites <- get_site()
head(all.sites)

ggplot(all.sites, aes(site.name,elev))+
  geom_point()

plot(density(all.sites$elev, from=0, na.rm=TRUE))

#List
all.datasets <- get_dataset()

#Web browser view
browse(all.datasets$`31`)

# North Dakota/MN 48.859419, -97.694836
# Maine 47.034696, -68.295424
# Eastern TX 30.107257, -94.380886
# North Florida 30.107257, -94.380886
eastern.us <- get_dataset(loc = c(-97.69, 30, -68, 49)) #6262 records

eastern.us.download <- get_download(eastern.us)

eastern.us.counts <- lapply(eastern.us.download, function(x){
  out <- cbind(x$counts, "lon"= x$dataset$site$long,
        "lat" = x$dataset$site$lat, "elev" = x$dataset$site$elev)
  out <- data.frame(out)
  out
})

class(eastern.us.counts[[3]])

east.counts <- do.call(rbind.fill, eastern.us.counts)

head(east.counts)

save(list="east.counts", file="P:/hackathon/NIMBioSPopSize/EasternUS_counts.Rdata")
```


